\textbf{On the (non-)exhaustivity of naturally occurring \whqs}

### 2022-11-14 analysis/03_experiment/rscripts/pre-processing.Rmd
violin plots

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(tidyverse)
# library(Hmisc)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin-raw.pdf",width=4,height=2)
```

@@

data_summary(agr)

@@

View(sum)

>>>>

```{r setup, include=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
library(lme4)
library(lmerTest)
library(multcomp) # not available for this version of R
library(tidyverse)
library(Hmisc)
theme_set(theme_bw())
cbPalette <- c("#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73","#56B4E9", "#D55E00", "#009E73","#999999", "#E69F00","#009E73")
this.dir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(this.dir)
source("../../helpers.R")
```

@@

@@

stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data = fun, geom = geom, width = 0.2, ...)
}

ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    # geom_jitter(shape=16, position=position_jitter(0.2)) +
    # geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
    stat_summary(fun.data = data_summary, geom = "pointrange",
                # width = 0.2) +
  # stat_sum_df("mean_cl_boot", mapping = aes(paraphrase))
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin-raw.pdf",width=4,height=2)
```

# data_summary(agr)

@@

# View(sum)

### 2022-11-14 papers/article/main.tex
violin plots

In this paper, we presented a series of studies looking at the naturalistic distribution of \whq meanings. We surveyed the literature, identifying three main linguistic factors that have been observed to modulate

>>>>

In this paper, we presented a series of studies looking at the naturalistic distribution of \whq meanings. We surveyed the literature, identifying three main linguistic factors that have been observed to modulate the interpetation of \whqs, and the main theoretical treatments of both the semantics of \whqs and of mention-some in particular. We

We then presented a series of studies that tested the reliability of these cues to interpretation using a paraphrase rating task to measure the perceived possible interpretations.

We created a database of \whqs from the switchboard corpus of telephone conversations, and from that generated our experimental stimuli. We then crowd-sourced

Experiment 1a and 1b tested the interpretation of root and embedded questions embedded in the 10 preceding lines of discourse from the corpus. Experiments 2a and 2b tested root and embedded questions using the same method but without the preceding discourse. Finally, we conducted an analysis of the effect of context on the distribution of perceived meanings.

We found that
